Winter 2025 ToDo

### 2025-12-09 Relations/Paper/Winter_2025_TODO.tex
Todo update

\end{todolist}
\section*{Research items}
\begin{todolist}
  \item (Research item) Find a concrete application of generalized Newman's Lemma. * Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).  
  \item (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
  \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle.   (This is what we were working on end of day 4th December).
  \end{todolist}
\end{document}

>>>>

\end{todolist}
\section*{Research items}
\begin{todolist}
  \item (Research item) Find a concrete application of generalized Newman's Lemma. * Finding a term rewrite system where it's easier to see that it is weakly cr and that every term is SM (as opposed to being CR).  
  \item (Research item) Formalize a first order term rewriting system. Use TeReSe to create a list of rewrite systems.
  \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counterexamples been shown before?
  \item (Research item) Work on the missing implications from the paper. So far we believe this is just CR $\to$ CP in the ARS section. - Will probably be quite a bit of work (low priority)
  \item (Research item) Investigate: what we've done for natural numbers could be done for an arbitrary ARS (in the counter examples files), but for weak minimality and weak excluded middle.   (This is what we were working on end of day 4th December).
  \end{todolist}

\section*{Week starting 8th December}
\begin{todolist}
  \item Is the new definition of wdec in Predicates correct? It corresponds to the definition in FBranching. (Do we want to go through and update all uses of Wdec with the new definition if it is correct?)
  \item Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations.  
\end{todolist}

\end{document}
